HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-03-18 paper/main.tex
minor

There are however a number of other serious consequences on focusing on verbal
predicates. We conducted an analysis of the English UCCA Wikipedia
corpus (5324 sentences)
in order to assess the impact of the following problems: 
\\
\begin{inparadesc}
\item[Copula clauses] are treated in HMEANT simply as instances of the main verb ``be'', which
generally does not convey the meaning of these clauses. They appear in 21.7\% of the sentences,
according to conservative estimates that only considers non-auxiliary instances of ``be''.
\\
\item[Nominal argument structures,] which are ignored by  HMEANT are in fact highly
pervasive, appearing in 48.7\% of the sentences.
\\
\item[Linkers] expressing an inter-relation between
clauses (mainly discourse markers and coordinating conjunctions) appear in 56\% of the
sentences\footnote{Argument structures and linkers are explicitly marked in UCCA. We identified non-auxiliary instances of ``be'' and nouns using the NLTK standard tagger. Nominative argument structures are here defined as Scenes whose main relation is headed by a noun.}.
\end{inparadesc}

@@

%Another example where a linker is omitted in translation:
%the source \equo{However, this review\dots}, which was translated as \equo{Diese
%\"Uberpr\"ufung\dots} (lit. \equo{This review}).
%This omission will not be taken into account by HMEANT at all.

@@

In HMEANT, there are no guidelines as to when to propagate and error. In HUME,
errors are localised as much as possible to where they occur, by the separation of atomic and structural nodes. This allows us to calculate more accurately the total score of the sentence.

>>>>

There are however a number of other serious consequences on focusing on verbal
predicates. We conducted an analysis of the English UCCA Wikipedia
corpus (5324 sentences)
in order to assess the impact of the following problems: 
\\
\begin{inparadesc}
\item[Copula clauses] are treated in HMEANT simply as instances of the main verb ``be'', which
generally does not convey the meaning of these clauses. They appear in 21.7\% of the sentences,
according to conservative estimates that only considers non-auxiliary instances of ``be''.
\\
\item[Nominal argument structures,] which are ignored by  HMEANT are in fact highly
pervasive, appearing in 48.7\% of the sentences.
\\
\item[Linkers] expressing an inter-relation between
clauses (mainly discourse markers and coordinating conjunctions) appear in 56\% of the
sentences, but ignored by HMEANT.
An example where a linker is omitted in translation in our experiments is
with the source \equo{However, this review\dots}, which was translated to
the German \equo{Diese \"Uberpr\"ufung\dots} (lit. \equo{This review}).
This omission will not be taken into account by HMEANT at all\footnote{Argument structures and linkers are explicitly marked in UCCA. We identified non-auxiliary instances of ``be'' and nouns using the NLTK standard tagger. Nominative argument structures are here defined as Scenes whose main relation is headed by a noun.}.
\end{inparadesc}

@@

@@

In HMEANT, there are no guidelines as to when to propagate an error. In HUME,
errors are localised as much as possible to where they occur,
by the separation of atomic and structural nodes.
This allows us to calculate more accurately the total score of the sentence.
